Formalizing Stack Safety as a Security Property

### 2022-12-04 submission5/noexceptions.tex
Cited Skorstengaard

  Our security semantics has similarities to the overlay semantics that have been proposed
  to characterize stack safety in the past~\cite{??}, but, like the basic machine
  semantics, it is not safe-by-construction. Rather, it gives us a means to \emph{define}
  the security properties that a correct enforcement scheme should implement, using
  some combination of hardware and software.

>>>>

  Our security semantics has similarities to the overlay semantics that have been proposed
  to characterize stack safety in the past~\cite{SkorstengaardSTK}, but, like the basic machine
  semantics, it is not safe-by-construction. Rather, it gives us a means to \emph{define}
  the security properties that a correct enforcement scheme should implement, using
  some combination of hardware and software.
